### 2008-11-10 doc/a-rex/arex_tech_doc.tex
submiting → submitting

\begin{itemize}
\item \textbf{Accepted} -- In this state the job has been submitted to a
CE but is not processed yet. The A-REX will analyze the JD and move
to the next stage. If the JD can not be processed the job will be
canceled and moved to the state \textbf{Finishing}.
\item \textbf{Preparing} -- The input data is being gathered in the SD (stage-in).
The A-REX is downloading the files specified in the JD and is waiting
for files which are supposed to be uploaded by the UI. If all files
are successfully gathered the job moves to the next state. If \textbf{any}
file can't be downloaded or it takes the UI too long to upload a file,
the job moves to \textbf{Finishing} state. It is possible to put a
limit on the number of simultaneous \textbf{Preparing} jobs. If this
limit is exceeded, jobs ready to enter the \textbf{Preparing} state
 will stay in the \textbf{Accepted} state, but prefixed with the PENDING:
mark. Exceptions are jobs which have no files to be downloaded. These
are processed out of limits.
\item \textbf{Submiting} -- The job is being passed for execution to the
\emph{Local Resource Management System} (LRMS). The corresponding
backends for many LRMSs are provided with the default installation.
If the local job submission is successful the job moves to the \textbf{Executing}
state. Otherwise it moves to \textbf{Finishing}. It is possible to
limit the aggregate number of jobs in \textbf{Submiting} and \textbf{Executing}
states.
\item \textbf{Executing} -- The job is queued or being executed in the LRMS.
The A-REX takes no actions except waiting until the job finishes.
\item \textbf{Killing} -- Necessary action to cancel the job in the LRMS
is being taken.
\item \textbf{Finishing} -- The output data is being processed (stage-out).
Specified data files are moved to the specified SEs and are optionally
registered at an Indexing Service. The user can download data files
from the SD by using the UI or other adequate tool. All the files
not specified as output files are removed from the SD at very beginning
of this state. It is possible to limit number of simultaneous jobs
in this state.
\item \textbf{Finished} -- No more processing is performed by the A-REX.
The user can continue to download data files from the SD. The SD is
kept available for some time (default is 1 week). After that the job
is moved to the state \textbf{Deleted}. The 'deletion' time can be
obtained by querying the Information Interface of the A-REX. If a
job was moved to \textbf{Finished} because of failure, it may be restarted
on request of a client. When restarted, a job is moved to the state
previous to the one in which it failed and is assigned mark PENDING.
This is needed in order to not break the configuration limits. Exception
is a job failed in \textbf{Executing} state and lacking input files
specified in JD. Such a job is treated like failed in \textbf{Preparing}
state.
\item \textbf{Deleted} -- The job is moved to this state if the user have
not requested job to be cleaned before the SD's lifetime expires.
Only minimal subset of information about such job is kept. The SD
is not available anymore.
\end{itemize}
In case of a failure special processing is applied to output files.
All specified output files are treated as \textbf{downloadable by
the user}. No files will be moved to their destination SE.

@@

\begin{tabular}{|>{\centering}p{0.15\columnwidth}|>{\centering}p{0.15\columnwidth}|>{\centering}p{0.2\columnwidth}|p{0.4\columnwidth}|}
\hline 
Applicable BES State&
ARC Sub-state&
A-REX internal state&
Description\tabularnewline
\hline
\hline 
\multirow{2}{*}{Pending}& Accepting& ACCEPTED &
Job is in the process of being submitted. This state is not recognised
by the A-REX yet. \emph{Accepted} is first reported state\\ \cline{2-4}
&Accepted& ACCEPTED& Job was submitted\\ \hline 
\multirow{8}{*}{Running}& Preparing& PREPARING& Stage-in process is going on\\ \cline{2-4} 
&Prepared& PREPARING + PENDING& Stage-in process has finished\\ \cline{2-4} 
&Submiting& SUBMIT& Communication with local batch system is in process\\ \cline{2-4} 
&Queued& INLRMS&
Job entered local batch system but is not runnning now. This state
is not recognised by the A-REX yet. \emph{Executing} is reported instead\\ \cline{2-4} 
&Executing& INLRMS& Job is being executed in local batch system\\ \cline{2-4} 
&Executed& INLRMS, INLRMS + PENDING&
Job execution in local batch system has finished. The A-REX dos not
detect job states inside local batch system yet. As result this state
is reported only if job is \emph{Pending}.\\ \cline{2-4} 
&Killing& CANCELING& Communication with local batch system to terminate execution is in process\\ \cline{2-4} 
&Finishing& FINISHING& Stage-out process is going on\\ \hline 
Cancelled& Killed& FINISHED&
Job was stopped by explicit user request. The A-REX currently does
not remember this request. \emph{Failed} is reported instead.\\ \hline 
Failed& Failed& FINISHED& There was a failure during execution\\ \hline 
Finished& Finished& FINISHED& Job finished successfully\\ \hline 
Finished& Deleted& DELETED& Job finished and was left in A-REX too long\\ \hline 
All& Pending& PENDING&
Job is prevented from going to the next state due to some internal
limits; this sub-state appears in parallel with other sub-states\\ \hline 
All& Held& &
Job processing is suspended on client request; this sub-state appears
in parallel with other sub-states. This state is reserved for future
and is not implemented yet.\\ \hline
\end{tabular}
\end{table}

@@

          <xsd:enumeration value=\char`\"{}Submiting\char`\"{}/>

>>>>

\begin{itemize}
\item \textbf{Accepted} -- In this state the job has been submitted to a
CE but is not processed yet. The A-REX will analyze the JD and move
to the next stage. If the JD can not be processed the job will be
canceled and moved to the state \textbf{Finishing}.
\item \textbf{Preparing} -- The input data is being gathered in the SD (stage-in).
The A-REX is downloading the files specified in the JD and is waiting
for files which are supposed to be uploaded by the UI. If all files
are successfully gathered the job moves to the next state. If \textbf{any}
file can't be downloaded or it takes the UI too long to upload a file,
the job moves to \textbf{Finishing} state. It is possible to put a
limit on the number of simultaneous \textbf{Preparing} jobs. If this
limit is exceeded, jobs ready to enter the \textbf{Preparing} state
 will stay in the \textbf{Accepted} state, but prefixed with the PENDING:
mark. Exceptions are jobs which have no files to be downloaded. These
are processed out of limits.
\item \textbf{Submitting} -- The job is being passed for execution to the
\emph{Local Resource Management System} (LRMS). The corresponding
backends for many LRMSs are provided with the default installation.
If the local job submission is successful the job moves to the \textbf{Executing}
state. Otherwise it moves to \textbf{Finishing}. It is possible to
limit the aggregate number of jobs in \textbf{Submitting} and \textbf{Executing}
states.
\item \textbf{Executing} -- The job is queued or being executed in the LRMS.
The A-REX takes no actions except waiting until the job finishes.
\item \textbf{Killing} -- Necessary action to cancel the job in the LRMS
is being taken.
\item \textbf{Finishing} -- The output data is being processed (stage-out).
Specified data files are moved to the specified SEs and are optionally
registered at an Indexing Service. The user can download data files
from the SD by using the UI or other adequate tool. All the files
not specified as output files are removed from the SD at very beginning
of this state. It is possible to limit number of simultaneous jobs
in this state.
\item \textbf{Finished} -- No more processing is performed by the A-REX.
The user can continue to download data files from the SD. The SD is
kept available for some time (default is 1 week). After that the job
is moved to the state \textbf{Deleted}. The 'deletion' time can be
obtained by querying the Information Interface of the A-REX. If a
job was moved to \textbf{Finished} because of failure, it may be restarted
on request of a client. When restarted, a job is moved to the state
previous to the one in which it failed and is assigned mark PENDING.
This is needed in order to not break the configuration limits. Exception
is a job failed in \textbf{Executing} state and lacking input files
specified in JD. Such a job is treated like failed in \textbf{Preparing}
state.
\item \textbf{Deleted} -- The job is moved to this state if the user have
not requested job to be cleaned before the SD's lifetime expires.
Only minimal subset of information about such job is kept. The SD
is not available anymore.
\end{itemize}
In case of a failure special processing is applied to output files.
All specified output files are treated as \textbf{downloadable by
the user}. No files will be moved to their destination SE.

@@

\begin{tabular}{|>{\centering}p{0.15\columnwidth}|>{\centering}p{0.15\columnwidth}|>{\centering}p{0.2\columnwidth}|p{0.4\columnwidth}|}
\hline 
Applicable BES State&
ARC Sub-state&
A-REX internal state&
Description\tabularnewline
\hline
\hline 
\multirow{2}{*}{Pending}& Accepting& ACCEPTED &
Job is in the process of being submitted. This state is not recognised
by the A-REX yet. \emph{Accepted} is first reported state\\ \cline{2-4}
&Accepted& ACCEPTED& Job was submitted\\ \hline 
\multirow{8}{*}{Running}& Preparing& PREPARING& Stage-in process is going on\\ \cline{2-4} 
&Prepared& PREPARING + PENDING& Stage-in process has finished\\ \cline{2-4} 
&Submitting& SUBMIT& Communication with local batch system is in process\\ \cline{2-4} 
&Queued& INLRMS&
Job entered local batch system but is not runnning now. This state
is not recognised by the A-REX yet. \emph{Executing} is reported instead\\ \cline{2-4} 
&Executing& INLRMS& Job is being executed in local batch system\\ \cline{2-4} 
&Executed& INLRMS, INLRMS + PENDING&
Job execution in local batch system has finished. The A-REX dos not
detect job states inside local batch system yet. As result this state
is reported only if job is \emph{Pending}.\\ \cline{2-4} 
&Killing& CANCELING& Communication with local batch system to terminate execution is in process\\ \cline{2-4} 
&Finishing& FINISHING& Stage-out process is going on\\ \hline 
Cancelled& Killed& FINISHED&
Job was stopped by explicit user request. The A-REX currently does
not remember this request. \emph{Failed} is reported instead.\\ \hline 
Failed& Failed& FINISHED& There was a failure during execution\\ \hline 
Finished& Finished& FINISHED& Job finished successfully\\ \hline 
Finished& Deleted& DELETED& Job finished and was left in A-REX too long\\ \hline 
All& Pending& PENDING&
Job is prevented from going to the next state due to some internal
limits; this sub-state appears in parallel with other sub-states\\ \hline 
All& Held& &
Job processing is suspended on client request; this sub-state appears
in parallel with other sub-states. This state is reserved for future
and is not implemented yet.\\ \hline
\end{tabular}
\end{table}

@@

          <xsd:enumeration value=\char`\"{}Submitting\char`\"{}/>
